##obtained from: https://www.youtube.com/watch?v=sEF1stn9ZwY


## Load libraries

Firstly, let's load the libraries that we will use.

They will need to be installed first if you don't already have them.

```{r}
#install.packages('writexl')
library(writexl)
#install.packages("RNetCDF")
library(RNetCDF)
```


## Loading the data

```{r}
data <- open.nc("E:\\duPontavice_bottom_temp_data\\bottom_temp_combined_product_1959-2021.nc")
print.nc(data)
```

At a glance, we can see it has 2 dimensions; they denote that there are 168 depth points and 36 characters (NCHAR).

There are 2 coordinate variables, with the same name as the dimensions. 

There are 4 data variables. The CHLOROPHYLL_A, FILTERED_VOLUME and PHAEOPIGMENT variables all have depth as their dimension. This means that the first chlorophyll a value corresponds to the first depth value.

The EVENT_ID has two dimensions, DEPTH and NCHAR. This is therefore a 2 dimensional array. This tells us that there is a maximum of one EVENT_ID for each of the 168 depths, and it has 36 characters - though variables can have missing values, denoted using a fill value. More on this later.

Finally, we have a long list of global attributes.

## A closer look

We can access a variable attribute like this:
  
  ```{r}
att.get.nc(data, "latitude", "units")
```

Let's write our data out as a variable we can easily use later:

```{r}
lat <- var.get.nc(data, "latitude")
lon <-  var.get.nc(data, "longitude")

memory.limit(55000) #increase memeory because bottom temp is huge (20+GB)
bottom_temp <-  var.get.nc(data, "bottomT")

time_data <-  var.get.nc(data, "time")



```


Create a dataframe. 

```{r}
df <- data.frame(Latitude = lat, Longitude = lon, BottomTemp = bottom_temp, Time = time_data)
df
```

Let's remove the rows with NAs

```{r}
df <- na.omit(df)
df
```

And then to output

```{r}
write_xlsx(df, '/home/lukem/chlorophyll_a_data_20191210_P2.xlsx')
```








```{r}

library(raster)
filename = "E:\\duPontavice_bottom_temp_data\\bottom_temp_combined_product_1959_2022_v1.nc"

s=stack(filename, varname="bt_temp")
```

##
BELOW SNIP IS FROM HUBERT FOR ACCESSING SPECIFIC DATA BY DAY AND YEAR

```{r}
library(tidync)

filename = "E:\\duPontavice_bottom_temp_data\\bottom_temp_combined_product_1959_2022_v1.nc"

data <- tidync::tidync(filename) %>%
  tidync::hyper_filter(year=year%in%(2020:2021), day=day%in%(c((0:104),(200:999)))) %>%
  tidync::hyper_tibble() %>%
  as.data.frame() 


#metadata info:
library(ncdf4)
nc_open(filename)

```
























